AFQ-Insight

### 2019-02-09 reports/manuscript/sections/introduction.tex
Remove cruft.
A bit more about what we're doing here.

\begin{itemize}

@@

\begin{enumerate}
\item Mass univariate approaches: In this approach comparisons between groups or
across individuals are done at each node of each tract, for each one of the
diffusion metrics available at that point. This approach is exhaustive, but the
challenge with this approach is that the are multiple points to compare, and
statistical power is compromised by a multiple comparison problem. Different
approaches can be taken to resolving this challenge. For example, Colby and
colleagues \cite{colby2012} used a non-parametric resmapling approach to correct
for family-wise error across the universe of different comparisons available in
the mass univariate approach \cite{Nichols2002-zu, Nichols2003-yy}.
\item ROI-based approach: An alternative is using an ROI based approach. In this
approach, the multiple comparison problem is circumvented by selecting just a
few tracts to compare in each individual, or even focusing on particular
segments of these tracts. This approach is very powerful when the biological
basis of the process of interest is relatively well understood (for a recent
example, see \cite{huber2018rapid}).
\item ROI-based selection, followed by multivariate analysis. Here, an ROI is
selected based on \emph{a priori} knowledge, and all the nodes or voxels in the
ROI are used together to fit a model that can predict differences between
individuals.
\end{enumerate}

In the present work, we present a novel framework for analysis of tractometry
that simultaneously selects the features for analysis, and fits a model to these
features. Rather than a comparative approach, this framework takes a predictive
approach to analysis \cite{Yarkoni2017-bi}. Using this approach, we need to
first deal with the large and asymmetric dimensionality of the data: tractometry
data usually has many more features (i.e., number of measurements per
individual) than samples (number of subjects). This regime is the target of
several statistical learning techniques, and is often solved by various forms of
regularization. For example, Tikhonov regularization shrinks the solution such that
each feature. The Lasso. One of the enabling

>>>>

@@

\begin{enumerate}

\item Mass univariate approaches: In this approach comparisons between groups or
across individuals are done at each node of each tract, for each one of the
diffusion metrics available at that point. This approach is exhaustive, but the
challenge with this approach is that the are multiple points to compare, and
statistical power is compromised by a multiple comparison problem. Different
approaches can be taken to resolving this challenge. For example, Colby and
colleagues \cite{colby2012} used a non-parametric resmapling approach to correct
for family-wise error across the universe of different comparisons available in
the mass univariate approach \cite{Nichols2002-zu, Nichols2003-yy}.

\item ROI-based approach: An alternative is using an ROI based approach. In this
approach, the multiple comparison problem is circumvented by selecting just a
few tracts to compare in each individual, or even focusing on particular
segments of these tracts. This approach is very powerful when the biological
basis of the process of interest is relatively well understood (for a recent
example, see \cite{huber2018rapid}).

\item ROI-based selection, followed by multivariate analysis. Here, an ROI is
selected based on \emph{a priori} knowledge, and all the nodes or voxels in the
ROI are used together to fit a model that can predict differences between
individuals.

\end{enumerate}

In the present work, we present a novel framework for analysis of tractometry
that simultaneously selects the features for analysis, and fits a model to these
features. Rather than a comparative approach, this framework takes a predictive
approach to analysis \cite{Yarkoni2017-bi}. We use a linear modeling approach,
which aims to predict phenotypical variance in a group of subjects, based on a
linear combination of the features estimated with tractometry. Using this
approach, we need to first deal with the large and asymmetric dimensionality of
the data: tractometry data usually has many more features (i.e., number of
measurements per individual) than samples (number of subjects), which makes
inferences from the data about phenotypical differences between individuals
ill-posed. This regime is the target of several statistical learning techniques,
and is often solved by various forms of regularization. For example, Tikhonov
regularization shrinks the solution such that the sum of squared contributions
from the individual features are minimized \cite{Hoerl2000-ij}. Another solution
to the problem is provided by the Lasso algorithm, which instead minimizes the
sum of the absolute values of contributions of each feature
\cite{Tibshirani1996-qs}. This tends to shrink to zero the contributions of many
of the features, providing results that are both accurate and interpretable.
When additional structure is available in the organization of the data,
regularization algorithms can take advantage of this structure. For example, if
the features lend themselves to a natural division into different groups, the
group lasso (GL) can be used to select groups of features, rather than
individual features \cite{Yuan2006-ky}. The Sparse Group Lasso (SGL) elaborates
on this idea by providing control both of group sparsity, as well as overall
sparsity of the solutions \cite{simon2013sgl}. Because the features measured
with tractomery lend themselves to grouping based on the tracts from which each
measurement is taken, GL and SGL provide a useful tool linear model fitting in
problems of this form.
